### 2018-02-24 DASFAA_2018/CR/Gruba_final/01-intro.tex

\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users.
These users behave variously, knowledge of which is significant for various applications such as recommendation system and activity analysis.
Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.

>>>>

\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users~\cite{DBLP:journals/fcsc/MaLHLH16,DBLP:journals/tkde/DuanMAMH17,DBLP:conf/icde/HuAMH16}.
These users behave variously, knowledge of whom is significant for various applications such as recommendation system and activity analysis.
Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.
